Mamba vs SOTA for Vision Tasks\\ \thanks{$\dagger$ Equal contributions}

### 2024-05-01 paper/main.tex
paper

\section{Introduction}
The rapid advancement of deep learning has led to remarkable achievements in various domains, including computer vision, natural language processing, and speech recognition. However, this progress has been accompanied by a significant increase in the size and complexity of neural network models. State-of-the-art (SOTA) models often have several million or even billions of parameters, making them computationally expensive and challenging to deploy on resource-constrained devices \cite{modelSize}. This trend poses concerns regarding energy consumption and the feasibility of deploying these models on edge devices, which have limited memory and processing power.

Many SOTA models for vision tasks, such as image classification and segmentation, rely on architectures like Transformers \cite{dosovitskiy2021image}, U-Net \cite{ronneberger2015unet}, and ResNet \cite{he2016deep}. While these models have achieved impressive performance, they often come with a high parameter count. Transformers, in particular, have gained significant attention due to their ability to capture long-range dependencies and achieve superior results in various tasks \cite{vaswani2017attention}. However, the self-attention mechanism in Transformers scales quadratically with the input sequence length, making them computationally expensive and difficult to apply to long sequences or high-resolution images \cite{choromanski2020rethinking}. This motivates the development of models that can achieve low parameter counts, accurately model long dependencies, and have fast inference and training.

@@

\section{Current Vision Task SOTA}
Over the past decade, deep learning has revolutionized the field of computer vision, with various architectures achieving SOTA performance on tasks such as image classification and segmentation. Convolutional Neural Networks (CNNs)\cite{lecundocument} have been at the forefront of this revolution, with architectures like AlexNet \cite{krizhevsky2012imagenet}, VGGNet \cite{simonyan2014very}, and Inception \cite{szegedy2015going} pushing the boundaries of classification accuracy on large-scale datasets.

@@

One of the most significant advancements in CNNs came with the introduction of ResNet \cite{he2016deep}, which addressed the problem of vanishing gradients in deep networks by introducing residual connections. ResNets allowed for the training of much deeper networks, leading to improved performance on various vision tasks. The success of ResNet sparked a wave of research into more efficient and effective CNN architectures, such as MobileNet \cite{howard2017mobilenets}, EfficientNet \cite{tan2019efficientnet}, and RegNet \cite{radosavovic2020designing}.

@@

Despite the impressive performance of these SOTA models, they often come with a high computational cost and large number of parameters. The self-attention mechanism in transformers scales quadratically with the input sequence length, making them challenging to apply to long sequences or high-resolution images \cite{choromanski2020rethinking}. CNNs, while more efficient than transformers, still require a significant number of parameters to achieve SOTA performance, especially for complex tasks like segmentation.

@@

The above derivation was done with reference to \cite{mambaNotes}.

@@

Now, the kernel can be constructed from the convolutional form \eqref{eq:convolutionalform} and output $y$ can be computed.
\begin{align}
    \mbfb{K} & = (\mathbf{C}\mbfb{B}, \mathbf{C}\mbfb{A}\mbfb{B}, \ldots, \mathbf{C}\mbfb{A}^k\mbfb{B}, \ldots) \\
    y        & = x * \mbfb{K}
\end{align}
The above derivation was done with reference to \cite{mambaNotes}.
This convolution can be computed in parallel as $y_k$ does not depend on previous outputs.

@@

For this our analysis, we compare four models against our own developed ones. The models are U-Net\cite{ronneberger2015unet}, ResNet18 \cite{he2016deep}, ResNet50, U-Mamba\cite{U-Mamba}, and SegFormer\cite{xie2021segformer}. Below we explain our choices.
\subsection{U-Net}
The core idea behind U-Net is to complement a traditional contracting network with successive layers that replace pooling operations with upsampling operators. These upsampling layers aim to increase the resolution of the output. Subsequent convolutional layers can then learn to assemble a precise output based on this high-resolution information \cite{ronneberger2015unet}.
A key modification in the U-Net architecture is the inclusion of a large number of feature channels in the upsampling part. This allows the network to effectively propagate contextual information to higher resolution layers. As a result, the expansive path of the network becomes more or less symmetric to the contracting part, leading to a distinctive U-shaped architecture. To predict pixels at the border regions of the image, the missing context is extrapolated by mirroring the input image. This tiling strategy is crucial for applying the network to large images, as it circumvents resolution limitations imposed by GPU memory constraints \cite{ronneberger2015unet}. Due to its encoder-decoder architecture, skip connections, multi-scale feature extraction, and its efficiency, U-Net has been used in many denoising and diffusion models. For instance, DDPMs (Denoising Diffusion Probabilistic Models) use an architecture similar to U-Net for denoising and sample generation \cite{DBLP:journals/corr/abs-2006-11239} while the popular Stable Diffusion architecture uses a U-Net based architecture for the diffusion process \cite{rombach2021highresolution}. We have chosen to compare our novel segmentation architecture against the U-Net architecture due to its well-established reputation and widespread adoption in the field of medical image segmentation.

\subsection{ResNet}
We have also selected ResNet18 and ResNet50 as additional benchmarks. These architectures, introduced by He et al. in their seminal work "Deep Residual Learning for Image Recognition" \cite{he2016deep}, have revolutionized the field of deep learning by addressing the problem of vanishing gradients in deep neural networks. The key innovation in ResNets is the introduction of residual connections, which allow the network to learn residual functions with reference to the input layer, thereby facilitating the training of much deeper networks. ResNet18 and ResNet50, with 18 and 50 layers respectively, have been widely adopted in various computer vision tasks, including image classification, object detection, and segmentation. These models have demonstrated exceptional performance and generalization ability across diverse datasets. By comparing our proposed architecture against ResNet18 and ResNet50, we aim to assess its effectiveness in relation to these well-established and highly influential architectures. This comparison will provide valuable insights into the capabilities of our model and its potential to advance the state-of-the-art in image segmentation tasks.
\subsection{U-Mamba}
As our model takes much inspiration from the recently developed U-Mamba design \cite{U-Mamba}, we also choose to incorporate it in our comparison. U-Mamba addresses these limitations by introducing a novel hybrid CNN-SSM block that leverages the strengths of both architectures. The convolutional layers in the block are responsible for local feature extraction, while the State Space Sequence Models (SSMs) \cite{gu2022efficiently}, a new family of deep sequence models, are known for their strong capability in handling long sequences and capturing long-range dependencies. By integrating these two components, U-Mamba achieves a balance between local and global information processing, enabling it to effectively handle long-range dependencies in biomedical image segmentation tasks. Moreover, U-Mamba incorporates a self-configuring mechanism that allows it to automatically adapt to various datasets without manual intervention, enhancing its versatility and usability.
\subsection{SegFormer}
SegFormer \cite{xie2021segformer} is a transformer-based semantic segmentation model that employs a hierarchical structure and a novel attention mechanism called Efficient Self-Attention (ESA). The SegFormer architecture consists of a transformer encoder for capturing long-range dependencies and a lightweight All-MLP decoder for generating high-resolution segmentation masks. The ESA module reduces the computational complexity of self-attention by performing attention operations in a local window and aggregating global information through a depth-wise convolution. This allows SegFormer to efficiently process high-resolution images while capturing both local and global context. Moreover, SegFormer introduces a position-sensitive embedding scheme that encodes both spatial and channel-wise information, enhancing the model's ability to capture fine-grained details. By comparing U-Mamba against SegFormer, we aim to evaluate the effectiveness of our hybrid CNN-SSM approach in relation to the transformer-based segmentation mechanism employed by SegFormer. This comparison will provide insights into the strengths and weaknesses of both architectures and their ability to handle complex biomedical image segmentation tasks. Furthermore, it will help us understand the potential of transformer-based approaches and hybrid approaches in advancing the state-of-the-art in biomedical image segmentation.

\subsection{UltraLight VM-UNet}
The UltraLight VM-UNet \cite{ultralightvmunet} is a lightweight neural network architecture designed for skin lesion segmentation tasks. It is built upon the Vision Mamba module, which is a state-space model (SSM) that can efficiently handle long-range dependencies in sequences, making it well-suited for image segmentation tasks.

@@

Inspired by \cite{U-Mamba} and \cite{ultralightvmunet}, we sought to implement both models on a different problem: tumor segmentation.

@@

\subsection{UL-VM-UNet-v2}
In UL-VM-UNet-v2, the number of parallel branches in the Parallel Vision Mamba (PVM) block was increased from 4 to 8. This modification directly decreases the parameter count, further proving the idea proposed in the UltraLight VM-UNet paper \cite{ultralightvmunet} that processing features in parallel with reduced channel counts can significantly reduce parameters while maintaining performance. The channel list is the same as Ultra LightM-UNet's, [8,16,24,32,48,64].

@@

\subsection{Input Data}
To further demonstrate the viability and versatility of the Mamba architecture, we conducted experiments on the CIFAR-10 dataset \cite{krizhevsky2009learning}, a widely-used benchmark for image classification tasks. CIFAR-10 consists of 60,000 32x32 color images across 10 classes, with 6,000 images per class. The dataset is split into 50,000 training images and 10,000 test images.

@@

\begin{thebibliography}{00}
    \bibitem{brown2020language} T. B. Brown et al., "Language Models are Few-Shot Learners," arXiv:2005.14165 [cs.CL], 2020.
    \bibitem{dosovitskiy2021image} A. Dosovitskiy et al., "An Image is Worth 16x16 Words: Transformers for Image Recognition at Scale," arXiv:2010.11929 [cs.CV], 2021.
    \bibitem{ronneberger2015unet} O. Ronneberger, P. Fischer, and T. Brox, "U-Net: Convolutional Networks for Biomedical Image Segmentation," arXiv:1505.04597 [cs.CV], 2015.
    \bibitem{he2016deep} K. He, X. Zhang, S. Ren, and J. Sun, "Deep Residual Learning for Image Recognition," arXiv:1512.03385 [cs.CV], 2016.
    \bibitem{vaswani2017attention} A. Vaswani et al., "Attention Is All You Need," arXiv:1706.03762 [cs.CL], 2017.
    \bibitem{gu2022efficiently} A. Gu, K. Goel, and C. Ré, "Efficiently Modeling Long Sequences with Structured State Spaces," arXiv:2111.00396 [cs.LG], 2022.
    \bibitem{simonyan2014very} K. Simonyan and A. Zisserman, “Published as a conference paper at ICLR 2015 VERY DEEP CONVOLUTIONAL NETWORKS FOR LARGE-SCALE IMAGE RECOGNITION.” Available: https://arxiv.org/pdf/1409.1556
    \bibitem{szegedy2015going} C. Szegedy et al., “Going deeper with convolutions.” Available: https://arxiv.org/pdf/1409.4842
    \bibitem{howard2017mobilenets} A. Howard et al., “MobileNets: Efficient Convolutional Neural Networks for Mobile Vision Applications.” Available: https://arxiv.org/pdf/1704.04861
    \bibitem{tan2019efficientnet} M. Tan and Q. Le, “EfficientNet: Rethinking Model Scaling for Convolutional Neural Networks.” Available: https://arxiv.org/pdf/1905.11946
    \bibitem{radosavovic2020designing} I. Radosavovic, R. Kosaraju, R. Girshick, K. He, and P. Dollár, “Designing Network Design Spaces.” Accessed: Apr. 30, 2024. [Online]. Available: https://arxiv.org/pdf/2003.13678
    \bibitem{choromanski2020rethinking} K. Choromanski et al., “Published as a conference paper at ICLR 2021 RETHINKING ATTENTION WITH PERFORMERS.” Accessed: Apr. 30, 2024. [Online]. Available: https://arxiv.org/pdf/2009.14794
    \bibitem{cheng2017survey} Y. Cheng, D. Wang, P. Zhou, and T. Zhang, “IEEE SIGNAL PROCESSING MAGAZINE, SPECIAL ISSUE ON DEEP LEARNING FOR IMAGE UNDERSTANDING 1 A Survey of Model Compression and Acceleration for Deep Neural Networks.” Accessed: Apr. 30, 2024. [Online]. Available: https://arxiv.org/pdf/1710.09282
    \bibitem{hinton2015distilling} G. Hinton, O. Vinyals, and J. Dean, “Distilling the Knowledge in a Neural Network,” 2015. Accessed: Apr. 30, 2024. [Online]. Available: https://arxiv.org/pdf/1503.02531
    \bibitem{gu2020hippo} A. Gu, T. Dao, S. Ermon, A. Rudra, and C. Ré, "HiPPO: Recurrent Memory with Optimal Polynomial Projections," Advances in Neural Information Processing Systems, vol. 33, pp. 1474-1487, 2020.
    \bibitem{vaswani2023attention} A. Vaswani et al., "Attention Is All You Need," arXiv:1706.03762 [cs.CL], 2023.
    \bibitem{gu2023mamba} A. Gu and T. Dao, "Mamba: Linear-Time Sequence Modeling with Selective State Spaces," arXiv:2312.00752 [cs.LG], 2023.
    \bibitem{U-Mamba} J. Ma, F. Li, and B. Wang, "U-Mamba: Enhancing Long-range Dependency for Biomedical Image Segmentation," arXiv:2401.04722 [cs.CV], 2024.
    \bibitem{rombach2021highresolution} R. Rombach, A. Blattmann, D. Lorenz, P. Esser, and B. Ommer, "High-Resolution Image Synthesis with Latent Diffusion Models," arXiv:2112.10752 [cs.CV], 2021.
    \bibitem{DBLP:journals/corr/abs-2006-11239} J. Ho, A. Jain, and P. Abbeel, "Denoising Diffusion Probabilistic Models," CoRR, vol. abs/2006.11239, 2020. [Online]. Available: https://arxiv.org/abs/2006.11239
    \bibitem{ultralightvmunet} R. Wu, Y. Liu, P. Liang, and Q. Chang, “UltraLight VM-UNet: Parallel Vision Mamba Significantly Reduces Parameters for Skin Lesion Segmentation.” Accessed: Apr. 20, 2024. [Online]. Available: https://arxiv.org/pdf/2403.20035.pdf
    \bibitem{zhao2017pyramid} H. Zhao, J. Shi, X. Qi, X. Wang and J. Jia, "Pyramid Scene Parsing Network," 2017 IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2017, pp. 6230-6239, doi: 10.1109/CVPR.2017.660.
    \bibitem{dataset} “Brain MRI segmentation,” www.kaggle.com. https://www.kaggle.com/datasets/mateuszbuda/lgg-mri-segmentation
    \bibitem{xie2021segformer} E. Xie, W. Wang, Z. Yu, A. Anandkumar, J. Alvarez, and P. Luo, “SegFormer: Simple and Efficient Design for Semantic Segmentation with Transformers.” Available: https://arxiv.org/pdf/2105.15203.pdf
    \bibitem{krizhevsky2009learning} A. Krizhevsky, "Learning Multiple Layers of Features from Tiny Images," Tech Report, 2009.
    \bibitem{xie2017aggregated} S. Xie, R. Girshick, P. Dollár, Z. Tu, and K. He, "Aggregated Residual Transformations for Deep Neural Networks," arXiv:1611.05431 [cs.CV], 2017.
    \bibitem{krizhevsky2012imagenet} A. Krizhevsky, I. Sutskever, and G. E. Hinton, "ImageNet Classification with Deep Convolutional Neural Networks," Advances in Neural Information Processing Systems, vol. 25, 2012.
    \bibitem{lecundocument} Y. Lecun, L. Bottou, Y. Bengio and P. Haffner, "Gradient-based learning applied to document recognition," in Proceedings of the IEEE, vol. 86, no. 11, pp. 2278-2324, Nov. 1998, doi: 10.1109/5.726791.
    \bibitem{zhu2024vision} L. Zhu, B. Liao, Q. Zhang, X. Wang, W. Liu, and X. Wang, “Vision Mamba: Efficient Visual Representation Learning with Bidirectional State Space Model,” arXiv.org, Feb. 10, 2024. https://arxiv.org/abs/2401.09417   
    \bibitem{modelSize} H. Naveed et al., “A Comprehensive Overview of Large Language Models.” Available: https://arxiv.org/pdf/2307.06435
    \bibitem{mambaNotes} U. Jamil, “hkproj/mamba-notes,” GitHub, Apr. 27, 2024. https://github.com/hkproj/mamba-notes (accessed Apr. 30, 2024).
\end{thebibliography}

>>>>

\section{Introduction}
The rapid advancement of deep learning has led to remarkable achievements in various domains, including computer vision, natural language processing, and speech recognition. However, this progress has been accompanied by a significant increase in the size and complexity of neural network models. State-of-the-art (SOTA) models often have several million or even billions of parameters, making them computationally expensive and challenging to deploy on resource-constrained devices \cite{naveed2024comprehensive}. This trend poses concerns regarding energy consumption and the feasibility of deploying these models on edge devices, which have limited memory and processing power.

Many SOTA models for vision tasks, such as image classification and segmentation, rely on architectures like Transformers \cite{dosovitskiy2021image}, U-Net \cite{ronneberger2015unet}, and ResNet \cite{he2015deep}. While these models have achieved impressive performance, they often come with a high parameter count. Transformers, in particular, have gained significant attention due to their ability to capture long-range dependencies and achieve superior results in various tasks \cite{vaswani2023attention}. However, the self-attention mechanism in Transformers scales quadratically with the input sequence length, making them computationally expensive and difficult to apply to long sequences or high-resolution images \cite{choromanski2022rethinking}. This motivates the development of models that can achieve low parameter counts, accurately model long dependencies, and have fast inference and training.

@@

\section{Current Vision Task SOTA}
Over the past decade, deep learning has revolutionized the field of computer vision, with various architectures achieving SOTA performance on tasks such as image classification and segmentation. Convolutional Neural Networks (CNNs)\cite{lecundocument} have been at the forefront of this revolution, with architectures like AlexNet \cite{krizhevsky2012imagenet}, VGGNet \cite{simonyan2014deep}, and Inception \cite{szegedy2015going} pushing the boundaries of classification accuracy on large-scale datasets.

@@

One of the most significant advancements in CNNs came with the introduction of ResNet \cite{he2015deep}, which addressed the problem of vanishing gradients in deep networks by introducing residual connections. ResNets allowed for the training of much deeper networks, leading to improved performance on various vision tasks. The success of ResNet sparked a wave of research into more efficient and effective CNN architectures, such as MobileNet \cite{howard2017mobilenets}, EfficientNet \cite{tan2020efficientnet}, and RegNet \cite{radosavovic2020designing}.

@@

Despite the impressive performance of these SOTA models, they often come with a high computational cost and large number of parameters. The self-attention mechanism in transformers scales quadratically with the input sequence length, making them challenging to apply to long sequences or high-resolution images \cite{choromanski2022rethinking}. CNNs, while more efficient than transformers, still require a significant number of parameters to achieve SOTA performance, especially for complex tasks like segmentation.

@@

The above derivation was done with reference to \cite{Jamil}.

@@

Now, the kernel can be constructed from the convolutional form \eqref{eq:convolutionalform} and output $y$ can be computed.
\begin{align}
    \mbfb{K} & = (\mathbf{C}\mbfb{B}, \mathbf{C}\mbfb{A}\mbfb{B}, \ldots, \mathbf{C}\mbfb{A}^k\mbfb{B}, \ldots) \\
    y        & = x * \mbfb{K}
\end{align}
The above derivation was done with reference to \cite{Jamil}.
This convolution can be computed in parallel as $y_k$ does not depend on previous outputs.

@@

For this our analysis, we compare four models against our own developed ones. The models are U-Net\cite{ronneberger2015unet}, ResNet18 \cite{he2015deep}, ResNet50, U-Mamba\cite{ma2024umamba}, and SegFormer\cite{xie2021segformer}. Below we explain our choices.
\subsection{U-Net}
The core idea behind U-Net is to complement a traditional contracting network with successive layers that replace pooling operations with upsampling operators. These upsampling layers aim to increase the resolution of the output. Subsequent convolutional layers can then learn to assemble a precise output based on this high-resolution information \cite{ronneberger2015unet}.
A key modification in the U-Net architecture is the inclusion of a large number of feature channels in the upsampling part. This allows the network to effectively propagate contextual information to higher resolution layers. As a result, the expansive path of the network becomes more or less symmetric to the contracting part, leading to a distinctive U-shaped architecture. To predict pixels at the border regions of the image, the missing context is extrapolated by mirroring the input image. This tiling strategy is crucial for applying the network to large images, as it circumvents resolution limitations imposed by GPU memory constraints \cite{ronneberger2015unet}. Due to its encoder-decoder architecture, skip connections, multi-scale feature extraction, and its efficiency, U-Net has been used in many denoising and diffusion models. For instance, DDPMs (Denoising Diffusion Probabilistic Models) use an architecture similar to U-Net for denoising and sample generation \cite{ho2020denoising} while the popular Stable Diffusion architecture uses a U-Net based architecture for the diffusion process \cite{rombach2022highresolution}. We have chosen to compare our novel segmentation architecture against the U-Net architecture due to its well-established reputation and widespread adoption in the field of medical image segmentation.

\subsection{ResNet}
We have also selected ResNet18 and ResNet50 as additional benchmarks. These architectures, introduced by He et al. in their seminal work "Deep Residual Learning for Image Recognition" \cite{he2015deep}, have revolutionized the field of deep learning by addressing the problem of vanishing gradients in deep neural networks. The key innovation in ResNets is the introduction of residual connections, which allow the network to learn residual functions with reference to the input layer, thereby facilitating the training of much deeper networks. ResNet18 and ResNet50, with 18 and 50 layers respectively, have been widely adopted in various computer vision tasks, including image classification, object detection, and segmentation. These models have demonstrated exceptional performance and generalization ability across diverse datasets. By comparing our proposed architecture against ResNet18 and ResNet50, we aim to assess its effectiveness in relation to these well-established and highly influential architectures. This comparison will provide valuable insights into the capabilities of our model and its potential to advance the state-of-the-art in image segmentation tasks.
\subsection{U-Mamba}
As our model takes much inspiration from the recently developed U-Mamba design \cite{ma2024umamba}, we also choose to incorporate it in our comparison. U-Mamba addresses these limitations by introducing a novel hybrid CNN-SSM block that leverages the strengths of both architectures. The convolutional layers in the block are responsible for local feature extraction, while the State Space Sequence Models (SSMs) \cite{gu2022efficiently}, a new family of deep sequence models, are known for their strong capability in handling long sequences and capturing long-range dependencies. By integrating these two components, U-Mamba achieves a balance between local and global information processing, enabling it to effectively handle long-range dependencies in biomedical image segmentation tasks. Moreover, U-Mamba incorporates a self-configuring mechanism that allows it to automatically adapt to various datasets without manual intervention, enhancing its versatility and usability.
\subsection{SegFormer}
SegFormer \cite{xie2021segformer} is a transformer-based semantic segmentation model that employs a hierarchical structure and a novel attention mechanism called Efficient Self-Attention (ESA). The SegFormer architecture consists of a transformer encoder for capturing long-range dependencies and a lightweight All-MLP decoder for generating high-resolution segmentation masks. The ESA module reduces the computational complexity of self-attention by performing attention operations in a local window and aggregating global information through a depth-wise convolution. This allows SegFormer to efficiently process high-resolution images while capturing both local and global context. Moreover, SegFormer introduces a position-sensitive embedding scheme that encodes both spatial and channel-wise information, enhancing the model's ability to capture fine-grained details. By comparing U-Mamba against SegFormer, we aim to evaluate the effectiveness of our hybrid CNN-SSM approach in relation to the transformer-based segmentation mechanism employed by SegFormer. This comparison will provide insights into the strengths and weaknesses of both architectures and their ability to handle complex biomedical image segmentation tasks. Furthermore, it will help us understand the potential of transformer-based approaches and hybrid approaches in advancing the state-of-the-art in biomedical image segmentation.

\subsection{UltraLight VM-UNet}
The UltraLight VM-UNet \cite{wu2024ultralight} is a lightweight neural network architecture designed for skin lesion segmentation tasks. It is built upon the Vision Mamba module, which is a state-space model (SSM) that can efficiently handle long-range dependencies in sequences, making it well-suited for image segmentation tasks.

@@

Inspired by \cite{ma2024umamba} and \cite{wu2024ultralight}, we sought to implement both models on a different problem: tumor segmentation.

@@

\subsection{UL-VM-UNet-v2}
In UL-VM-UNet-v2, the number of parallel branches in the Parallel Vision Mamba (PVM) block was increased from 4 to 8. This modification directly decreases the parameter count, further proving the idea proposed in the UltraLight VM-UNet paper \cite{wu2024ultralight} that processing features in parallel with reduced channel counts can significantly reduce parameters while maintaining performance. The channel list is the same as Ultra LightM-UNet's, [8,16,24,32,48,64].

@@

\subsection{Input Data}
To further demonstrate the viability and versatility of the Mamba architecture, we conducted experiments on the CIFAR-10 dataset \cite{CIFAR-10}, a widely-used benchmark for image classification tasks. CIFAR-10 consists of 60,000 32x32 color images across 10 classes, with 6,000 images per class. The dataset is split into 50,000 training images and 10,000 test images.

@@

\bibliographystyle{ieeetr}
\bibliography{refs}
